\titlepage[Winterhold College]{%
November 2011\\
This thesis is submitted for the degree of Doctor of Philosophy%
}

\begin{abstract}
One may define a concept of an $n$-person game in which each player has a
finite set of pure strategies and in which a definite set of payments to the
$n$ players corresponds to each $n$-tuple of pure strategies, one strategy
being taken for each player.
\end{abstract}


\begin{singlespacing}
\begin{declaration}
\noindent
% Cambridge declaration.
This thesis is the result of my own work and includes nothing which is the
outcome of work done in collaboration, except as declared in the preface and
specified in the text.
%
It is not substantially the same as any work that has already been submitted
before for any degree or other qualification except as declared in the preface
and specified in the text.
%
It does not exceed the prescribed word limit for the
%
Physics and Chemistry
%
Degree Committee.
\vspace*{1cm}
\begin{flushright}
Patches~O'Houlihan
\end{flushright}
\end{declaration}
\end{singlespacing}


\begin{acknowledgements}
Hi mom.
This thesis template derives from `hepthesis'~\cite{hepthesis}.
\end{acknowledgements}


\begin{preface}
\begin{singlespacing}
\begin{epigraphs}
\qitem{%
Begin reading at Chapter N. Do \emph{not} read the quotations
that appear at the beginning of the chapter.%
}%
{Donald~E.~Knuth,
\textit{The Art of Computer Programming, Volume~1},
1975~\cite{knuth1975art}}
\end{epigraphs}
\end{singlespacing}
\noindent
Another abstract?

To write the tera-electron-volt unit with actually proper kerning, use commands
like \texttt{\$\,\textbackslash eV[T]\$}.
This allows both the `T' and the `V' to overlap with the `e' as in
$13\,\eV[T]$.
You can substitute the `T' for any prefix.
Use slashes after commands like \texttt{\textbackslash altas\textbackslash} to
ensure proper spacing.
Without the second slash, \atlas will stick to the next word.

\end{preface}

\afterpage{%
\phantomsection
\addcontentsline{toc}{chapter}{Contents}%
}
\tableofcontents

% the following blank page should also have no page number
\thispagestyle{empty}
